Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-22 analysis/paper/paper.Rmd
clarify caption
replace broad with wide

In an effort to understand where as a discipline we stand as plant pathologists regarding open science and reproducible research, we surveyed a broad selection of articles to represent a broad swathe of publications to evaluate our collective status.
We hand-picked 21 journals which we felt represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, applied and fundamental work, country of origin and ranking metrics, *e.g.* quartile range or citation index, to represent the discipline.
The aim was to gather as complete an overview of the status of computational reproducibility in plant pathology journals as possible and avoid bias in the findings by skewing towards high-impact journals that may have a greater influence.
From those 21 journals we randomly selected 450 articles published from 2012 to 2021.
Using R [@RCT2022], two lists were created, the first was a list of the 21 journals and the second was a list of the evaluators that were evaluating the articles for reproducibility.
Initially there were four evaluators, later a fifth was added and the list was recreated.
There were three evaluation events that took place to increase the yearly coverage of the evaluations.
Each evaluator was assigned 50 articles to evaluate during an evaluation event.
A list of randomly generated numbers representing page numbers from one to 150, sampled with replacement, was assigned to a randomized list of the 21 journals for each sampling event.
This was done because some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year.

@@

```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public. A test for equivalence was unable to detect any clear differences between *Phytopathology* and all other journals sharing computational materials. However, a test for equivalence found that *Molecular Plant Pathology* and *Phytopathologia Mediterranea* were more likely have data available than articles found in *Phytopathology*. Intervals in grey have a median value less than that of *Phytopathology*, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*. Intervals in black have a median value that is greater than that of *Phytopathlogy*, the base level for the analysis and articles in these journals could be more likely to share data or code than those found in *Phytopathology*.', cache=FALSE, fig.env='figure'}
a <- plot(parameters(m_f1)) +
  scale_colour_grey() +
  ggtitle("Code")

>>>>

In an effort to understand where as a discipline we stand as plant pathologists regarding open science and reproducible research, we surveyed a broad selection of articles to represent a wide swathe of publications to evaluate our collective status.
We hand-picked 21 journals which we felt represented research publications in the field of plant pathology (Table \@ref(tab:journals)) that encompassed a range of subject matter foci, applied and fundamental work, country of origin and ranking metrics, *e.g.* quartile range or citation index, to represent the discipline.
The aim was to gather as complete an overview of the status of computational reproducibility in plant pathology journals as possible and avoid bias in the findings by skewing towards high-impact journals that may have a greater influence.
From those 21 journals we randomly selected 450 articles published from 2012 to 2021.
Using R [@RCT2022], two lists were created, the first was a list of the 21 journals and the second was a list of the evaluators that were evaluating the articles for reproducibility.
Initially there were four evaluators, later a fifth was added and the list was recreated.
There were three evaluation events that took place to increase the yearly coverage of the evaluations.
Each evaluator was assigned 50 articles to evaluate during an evaluation event.
A list of randomly generated numbers representing page numbers from one to 150, sampled with replacement, was assigned to a randomized list of the 21 journals for each sampling event.
This was done because some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published since most journals start with page number one at the beginning of the year.

@@

```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public. A test for equivalence was unable to detect any clear differences between *Phytopathology* and all other journals sharing computational materials (code). However, a test for equivalence found that *Molecular Plant Pathology* and *Phytopathologia Mediterranea* were more likely have data available than articles found in *Phytopathology*. Intervals in grey have a median value less than that of *Phytopathology*, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*. Intervals in black have a median value that is greater than that of *Phytopathlogy*, the base level for the analysis and articles in these journals could be more likely to share data or code than those found in *Phytopathology*.', cache=FALSE, fig.env='figure'}
a <- plot(parameters(m_f1)) +
  scale_colour_grey() +
  ggtitle("Code")
